---
title: "Prediction"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

We load the data.

```{r}
training <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")
testing <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv")
```

We remove all columns that contain missing values, encoded by either NA or empty factor variables.
The prediction is supposed to use data from accelerometers on the belt, forearm, arm, and dumbell. So we only keep those predictors.
```{r }
training <- training[,!apply(training,2,function(x) any(is.na(x)) | any(as.character(x) == ""))]

training <- training[,grep("arm|belt|dumbbel|classe",names(training))]
```

## Training/Validation Split

Test the training set into the training set used for model training and a cross validation set. We use a 80/20 split.
```{r}
set.seed(20)
library(caret)
inTrain <- createDataPartition(training$classe, p = 0.8)[[1]]
trainingS <- training[ inTrain,]
validationS <- training[-inTrain,]
```

## Model Training

We train a SVM.
```{r}
library(e1071)
model <- svm(factor(classe) ~ . , data = trainingS)
```

## Model assessment

In sample confusion matrix
```{r }
confusionMatrix(trainingS$classe, predict(model))
```

Out of sample confusion matrix
```{r }
confusionMatrix(validationS$classe, predict(model,validationS))
```

The expected out of sample accuracy is 95%, the same as the cross validation accuracy.


